The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)

### 2018-12-02 README.Rmd
first changes after reviews

> Horta, P., Cascalheira, J., Bicho, N. (2018). _The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)_. Name of journal/book <https://doi.org/xxx/xxx>

@@

> Horta, P., Cascalheira, J., Bicho, N. (2018). _The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

This repository is organized as an R package using rrtools by Ben Marwick which can be installed from github with:

@@

>>>>

> Horta, P., Cascalheira, J., Bicho, N. (2018). _The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)_. Journal of Paleolithic Archaeology <https://doi.org/xxx/xxx>

@@

> Horta, P., Cascalheira, J., Bicho, N. (2018). _The role of lithic bipolar technology in Western Iberia’s Upper Paleolithic: the case of Vale Boi (southern Portugal)_. SocArXiv , Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

This repository is organized as an R package using rrtools by [Ben Marwick](https://github.com/benmarwick) which can be installed from github with:

git clone https://github.com/benmarwick/rrtools.git

The functions are provided as a package because this makes it simpler to reuse the functions many times in the paper. It also makes it easier for others to use and adapt these functions on their own data. Nevertheless, this package has been written explicitly for this project and may not yet be suitable for more general purpose use.

@@

If you want to re-run all the analyses in R, you can start by installing the compendium package with this line at the R prompt:

```{r eval = FALSE}

devtools::install_github("jmcascalheira/ScaledPiecesVB")

### 2018-12-02 analysis/paper/paper.Rmd
first changes after reviews

output: 
    bookdown::word_document2: #subsistute by pdf_document2 or hmtl_document2 as necessary
      fig_caption: yes
      reference_docx: "../templates/template2.docx" 
bibliography: ScaledPiecesVB.bib
csl: "../templates/springer-socpsych-author-date.csl"
---

@@

source('~/R_DATA/compendiums/ScaledPiecesVB/R/functions.R')

@@

library(knitr)
library(citr)
library(tidyverse)
library(broom)
library(FactoMineR)
library(factoextra)
library(ggpubr)
library(ggplot2)
library(ggrepel)
library(maptools)
library(ggmap)
library(devtools)
library(legendMap)
library(tab)
library(sjstats)
library(powerAnalysis)
library(epitools)
library(wesanderson)

#library(ScaledPiecesVB)

>>>>

output: 
    bookdown::word_document2: #substitute by pdf_document2 or hmtl_document2 as necessary
      fig_caption: yes
      reference_docx: "../templates/template2.docx" 
bibliography: ScaledPiecesVB.bib
csl: "../templates/springer-socpsych-author-date.csl"
---

@@

@@

library(knitr)
library(citr)
library(tidyverse)
library(broom)
library(FactoMineR)
library(factoextra)
library(ggpubr)
library(ggplot2)
library(ggrepel)
library(maptools)
library(ggmap)
library(devtools)
library(legendMap)
library(tab)
library(sjstats)
library(powerAnalysis)
library(epitools)
library(wesanderson)
library(ScaledPiecesVB)
